\documentclass[9pt,aspectratio=1610]{beamer}

\include{frontmacros}
\begin{document}


\title[Virtual XAFS School]{EXAFS Data Analysis with FEFF}
\author[M Newville]{Matthew Newville}
\date{July-2021}

\institute[Univ of Chicago]{Center for Advanced Radiation Sources\\
  The University of Chicago}

\begin{frame} \titlepage
  \vmm
  \begin{center}
    Fundamentals of X-ray Absorption Fine-Structure
  \end{center}

  \vmm

  \begin{cenpage}{60mm}
    Virtual XAFS School at Illinois Institute of Technology and Advanced
  Photon Source
\end{cenpage}
\end{frame}

\section{The EXAFS Equation}

 \input{slides/feff_xafseq1}
 \input{slides/modeling}
 \input{slides/fit_statistics}
 \input{slides/fitspace}
 \input{slides/modeling_2nd}
\section{Path Parameters}
 \input{slides/pathparams}
\section{Parameters and Constraints}
 \input{slides/constraints}
 \input{slides/model_cu_3temp}

\input{slides/disorder_terms}

\section{Conclusions}
\begin{slide}{EXAFS Data Analysis with FEFF}


  \begin{cenpage}{126mm}

    Using {\feff} to model EXAFS mostly means paying attention to:

    \begin{itemize}
    \item   $N_{\rm idp}$ -- not very many
      Parameters can be varied for a limited $k$ and $R$ range.
    \item   Always look at the uncertainties in the Parameters, not just
      best-fit values.
    \item   Check (or require in the fit) that $\sigma^2 > 0$,  $N > 0$.
    \item   Think about how you might combine Parameters for different
      Paths, ideally making a physical model.
    \item  Try a third cumulant now and then -- it might be needed.
    \item   For very disordered systems, cumulants might not be enough.
    \end{itemize}

        \vmm     \hrule \vmm

  More information on X-rays and X-ray Absorption Spectroscopy:

  \begin{itemize}
  \item[] {\Blue{https://xafs.xrayabsorption.org/}}
  \item[] {\BlueEmph{Fundamentals of XAFS}} M. Newville, Reviews in  Mineralogy \& Geochemistry {\bf{78}}, 2014.
  \item[] {\BlueEmph{Introduction to XAFS}} G. Bunker, Cambridge Univ  Press,  2010.
  \item[] {\BlueEmph{XAFS for Everyone}} S. Calvin, CRC Press, 2013.
  \item[]  {\BlueEmph{Elements of Modern X-ray Physics}}  J.~Als-Nielsen
    \& D.~McMorrow,  John Wiley \& Sons. 2001

  \end{itemize}

\end{cenpage}


 \vfill
\end{slide}



\end{document}
