\documentclass[9pt,aspectratio=1610]{beamer}

\include{frontmacros}
\begin{document}


\title[Virtual XAFS School]{Using FEFF for EXAFS Data Analysis}  %%  and FEFF fitting}
\author[M Newville]{Matthew Newville}
\date{July-2021}

\institute[Univ of Chicago]{Center for Advanced Radiation Sources\\
  The University of Chicago}

\begin{frame} \titlepage
  \vmm
  \begin{center}
    Fundamentals of X-ray Absorption Fine-Structure
  \end{center}

  \vmm

  \begin{cenpage}{60mm}
    Virtual XAFS School at Illinois Institute of Technology and Advanced
  Photon Source
\end{cenpage}
\end{frame}

\section{The EXAFS Equation (REVIEW)}

\input{slides/feff_xafseq}
\input{slides/feffpractice}
\input{slides/modeling}

% \input{slides/fit_statistics}
% \input{slides/fitspace}
% \input{slides/modeling_2nd}
% \input{slides/pathparams}
% \input{slides/constraints}
% \input{slides/model_cu_3temp}
% \input{slides/theory_conclusions}




\begin{slide}{Using FEFF for EXAFS Analysis}


  \begin{cenpage}{126mm}

    Using {\feff} to calculate the scattering factors does not need to be
    too hard.

    \begin{itemize}
    \item   Start with a crystal structure that close to your structure.
    \item   Make sure you have the absorbing element and edge right!
    \item    Pay attention to the {\RedEmph{degeneracy}}, or coordination number for    each path.
    \item    Don't be afraid to alter the atoms list in {\feffinp}, especially    replacing atom types or importing structures from simulations.
    \item    Don't be afraid to mix paths from different calculations.
    \item   Don't worry too much about the rest of it -- let the GUI programs    ({\xasviewer}, {\artemis}) help you manage these calculations.
    \end{itemize}

        \vmm     \hrule \vmm

  More information on X-rays and X-ray Absorption Spectroscopy:

  \begin{itemize}
  \item[] {\Blue{https://xafs.xrayabsorption.org/}}
  \item[] {\BlueEmph{Fundamentals of XAFS}} M. Newville, Reviews in  Mineralogy \& Geochemistry {\bf{78}}, 2014.
  \item[] {\BlueEmph{Introduction to XAFS}} G. Bunker, Cambridge Univ  Press,  2010.
  \item[] {\BlueEmph{XAFS for Everyone}} S. Calvin, CRC Press, 2013.
  \item[]  {\BlueEmph{Elements of Modern X-ray Physics}}  J.~Als-Nielsen
    \& D.~McMorrow,  John Wiley \& Sons. 2001

  \end{itemize}

\end{cenpage}


 \vfill
\end{slide}



\end{document}
