

\begin{slide}{The EXAFS Equation: Recap}


  \begin{cenpage}{120mm}

    Even with all those complications and caveats, we still use the
    {\BlueEmph{EXAFS Equation}}: \vspace{-1mm}

  \begin{center}
    \[ \chi(k) = \sum_j {\frac{{\Blue{N_j}} {\Red{f_j(k)}}
        e^{-2{\Blue{R_j}}/{\Red{\lambda(k)}}}
        e^{-2k^2{\Blue{\sigma_j^2}}}}{k{\Blue{R_j}}^2}
      {\sin[{2k{\Blue{R_j}} + {\Red{\delta_j(k)}}] }}} \]
  \end{center}

  \vmm

  where $\Red{f(k)}$ and $\Red{\delta(k)}$ are
  {\RedEmph{photo-electron scattering properties}} of the neighboring
  atom and $ \Red{\lambda(k)} $ is the photo-electron mean-free-path.

  \vmm


  \vmm
Again, if we know these properties, we can determine:
  \onslide+<2->
    \begin{description}
      \settowidth{\labelwidth}{15mm}
      \setlength{\itemindent}{15mm}
      \setlength{\leftmargin}{15mm}
    \item[$R$] distance to neighboring atom.
    \item[$N$] coordination number of neighboring atom.
    \item[$\sigma^2$] mean-square disorder of neighbor distance \par
      \hspace{13.5mm} (or
      more complicated disorder terms).
    \end{description}

  \vmm
  \onslide+<3>
  ${\Red{f(k)}}$ and ${\Red{\delta(k)}}$ depend on atomic number
  {\BlueEmph{Z}} of the scattering atom, so we can also determine the
  species of the neighboring atom.

\end{cenpage}

\end{slide}


\begin{slide}{EXAFS Theory  Conclusions:}
  
  \begin{cenpage}{110mm}
    We have an EXAFS Equation that we can use to model EXAFS data.

  \begin{center}
    \[ \chi(k) = \sum_j {\frac{{\Blue{N_j}} {\Red{f_j(k)}}
        e^{-2{\Blue{R_j}}/{\Red{\lambda(k)}}}
        e^{-2k^2{\Blue{\sigma_j^2}}}}{k{\Blue{R_j}}^2}
      {\sin[{2k{\Blue{R_j}} + {\Red{\delta_j(k)}}] }}} \]
  \end{center}

  \vmm
  In later videos and demonstrations we'll show how to use this for
  analyzing EXAFS data.

  

  \vmm\vmm
  
  More information on X-rays and X-ray Absorption Spectroscopy:

  \begin{itemize}
  \item[] {\Blue{https://xafs.xrayabsorption.org/}}
  \item[] {\BlueEmph{Fundamentals of XAFS}} M. Newville, Reviews in  Mineralogy \& Geochemistry {\bf{78}}, 2014.
  \item[] {\BlueEmph{Introduction to XAFS}} G. Bunker, Cambridge Univ  Press,  2010.
  \item[] {\BlueEmph{XAFS for Everyone}} S. Calvin, CRC Press, 2013.
  \item[]  {\BlueEmph{Elements of Modern X-ray Physics}}  J.~Als-Nielsen
    \& D.~McMorrow,  John Wiley \& Sons. 2001
    
  \end{itemize}

\end{cenpage}


 \vfill
\end{slide}
 
